Structured matrix

### 2020-01-28 doc/fast_ssa/paper.tex
wirtinger derivative

{\bf Proof}:
$$
{\mathbfcal F}[x(t-t_0)]  = \int_{-\infty}^{\infty} x(t - t_0) e^{-i\omega t} dt  
$$
we set $t^{\prime} = t - t_0$ and exchange the variables, we can get
$$
{\mathbfcal F}[x(t-t_0)]  = \int_{-\infty}^{\infty} x(t^{\prime}) e^{-i\omega (t^{\prime} + t_0)} d t^{\prime}  $$
$$
{\mathbfcal F}[x(t-t_0)] = e^{i \omega t_0} \int_{-\infty}^{\infty} x(t^{\prime}) e^{-i\omega t^{\prime}} d t^{\prime} = X(\omega) e^{i \omega t_0}
$$

@@

>>>>

{\bf Proof}:
$$
{\mathbfcal F}[x(t-t_0)]  = \int_{-\infty}^{\infty} x(t - t_0) e^{-i\omega t} dt  
$$
we set $t^{\prime} = t - t_0$ and exchange the variables, we can get
$$
{\mathbfcal F}[x(t-t_0)]  = \int_{-\infty}^{\infty} x(t^{\prime}) e^{-i\omega (t^{\prime} + t_0)} d t^{\prime}  $$
$$
{\mathbfcal F}[x(t-t_0)] = e^{-i \omega t_0} \int_{-\infty}^{\infty} x(t^{\prime}) e^{-i\omega t^{\prime}} d t^{\prime} = X(\omega) e^{-i \omega t_0}
$$

@@

\section{Complex derivative}
Let $f(z, z^{\ast})$: $\mathbb{C} \times \mathbb{C} \rightarrow \mathbb{C}$ be a function of a complex variable $z$ and its complex conjugate $z^{\ast}$, where $z = x + iy$. We have the derivative 
\begin{equation}
\frac{\partial f}{\partial z} = \frac{1}{2}(\frac{\partial f}{\partial x} - i\frac{\partial f}{\partial x}),
\end{equation}
and
\begin{equation}
\frac{\partial f}{\partial z^{\ast}} = \frac{1}{2}(\frac{\partial f}{\partial x} + i\frac{\partial f}{\partial x}).
\end{equation}
Using the definition of complex derivative, it's clear that 
\begin{equation}
\begin{split}
\frac{\partial f}{\partial z} &= \left( \frac{\partial f}{\partial z^{\ast}} \right)^{\ast} \\
\frac{\partial z}{\partial z} &= 1 \\
\frac{\partial z^{\ast}}{\partial z^{\ast}} &= 1 \\
\frac{\partial z^{\ast}}{\partial z} &= 0
\end{split}.
\end{equation}
With above property, we can simply consider the complex variable and its complex conjugate $z^{\ast}$ as two independent variable.

\subsection{Stationary point}
Let $f(z, z^{\ast})$: $\mathbb{C} \times \mathbb{C} \rightarrow \mathbb{R}$ be a function mapping a complex variable $z$ and its complex conjugate $z^{\ast}$ to a real number. A sufficient and necessary condition for $f(z, z^{\ast})$ have a stationary point is $\frac{\partial f}{\partial z} = 0$. Similarly $\frac{\partial f}{\partial z^{\ast}} = 0$ is also a sufficient and necessary condition.

\subsection{Complex gradient}
Let's think about the first-order Taylor-series expansion, we have 
\begin{equation}
\delta f = \frac{\partial f}{\partial z} \delta z +  \frac{\partial f}{\partial z^{\ast}} \delta z^{\ast} 
\end{equation}
By using the property $\frac{\partial f}{\partial z} = \left( \frac{\partial f}{\partial z^{\ast}} \right)^{\ast}$, we can get 
\begin{equation}
\delta f = 2 Re (\frac{\partial f}{\partial z} \delta z),
\end{equation}
where the operator $Re$ means take the real part of the input.
We can extend this property to a function of a complex vector $g$: $\mathbb{C}^N \rightarrow \mathbb{R}$. We denote the complex vector as $\bf z$, so its first-order Taylor expansion can be expressed as
\begin{equation}
\begin{split}
\delta g &= 2 \sum_{i=1}^N Re \left(\frac{\partial g}{\partial z_i} \delta z_i \right) \\
             &= 2 Re\left( \left( \frac{\partial g}{\partial {\bf z}} \right)^T {\bf \delta z} \right)
\end{split}
\end{equation}
To make the above expression consistent with the axiom of inner product, we replace the above equation as 
\begin{equation}
\delta g = 2 Re \left( \left( \frac{\partial g}{\partial {\bf z^{\ast}}}\right)^H {\bf \delta z} \right)
\end{equation}
The maximum change $\delta g$ is obtained when $\delta {\bf z}$ is in the same direction of $\frac{\partial g}{\partial {\bf z^{\ast}}}$. It means that
\begin{equation}
\delta {\bf z} = \alpha \frac{\partial g}{\partial {\bf z^{\ast}}}.
\end{equation}
Where $\alpha$ is a real number indicate the magnitude of the vector $\delta {\bf z}$. This explanation suggest that the gradient vector $ \frac{\partial g}{\partial {\bf z^{\ast}}}$ is required for updating the variable ${\bf z}$ in an optimization problem.

\subsection{discrete time linear time invariant system}
We derive the mathematical model for describing discrete time linear invariant system. Suppose the input to a system is an impulse $\delta[n]$, which is equal to $1$ when $n=0$ and is $0$ elsewhere. The impulse response of this system is indicated by $h[n]$. The $\textbf{time invariant}$ property mean that the delayed impulse response is the output of the delayed impulse, which can be expressed as 
\begin{equation}
\delta[n-k] \rightarrow h[n-k],
\end{equation}
where $k$ indicate the number of samples delayed.

Any discrete-time signal(sequence) can be expressed as the weighted summation of delayed impulse as 
\begin{equation}
x[n] = \sum_{k=-\infty}^{+\infty} x[k] \delta[n-k]
\label{input}
\end{equation}
Combine with the linear property of this system, the output can be expressed as
\begin{equation}
y[n] = \sum_{k=-\infty}^{+\infty} x[k] h[n-k]
\end{equation}
Which give the definition of convolution which are used to describe the linear time-invariant system as $y[n] = x[n] \ast h[n]$.

Suppose the input is given as $g[n] = x[n-p_1]$ and the impulse response of the system is $f[n] = h[n-p_2]$. What is the output of this system? There are two ways to derive the result, one is based on the definition we given in equation (\ref{input}).
\begin{equation}
\begin{split}
g[n] &= \sum_{k=-\infty}^{+\infty} g[k] \delta[n-k] \\
       &= \sum_{k=-\infty}^{+\infty} x[k-p_1] \delta[n-k]
\end{split}
\end{equation}
The output of this system is
\begin{equation}
\begin{split}
s[n] &= \sum_{k=-\infty}^{+\infty} x[k-p_1] f[n-k] \\
       &= \sum_{k=-\infty}^{+\infty} x[k-p_1] h[n-k-p_2] \\
\end{split}
\label{sum}
\end{equation}
We can the variable change trick by setting $k^{\prime} = k-p_1$, so we have $k = k^{\prime} + p_1$. With this variable change, equation (\ref{sum}) can be reformulated as 
\begin{equation}
\begin{split}
s[n]  &= \sum_{k^{\prime}=-\infty}^{+\infty} x[k^{\prime}] h[n-k^{\prime}-p_1- p_2]    \\
        &= \sum_{k^{\prime}=-\infty}^{+\infty} x[k^{\prime}] h[(n-p_1- p_2)-k^{\prime}] \\
        &= y[n-p_1-p_2]
\end{split}
\label{sum}
\end{equation}
